---
title: "Infer Guide"
output:
  html_document: 
    code_folding: show
    toc: yes
    toc_float: yes
    toc_depth: 4
    theme: yeti
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = F)
```

We conduct simulation-based inference using the `tidymodels` package in R. `tidymodels` a meta package (similar to `tidyverse`), such that mutliple packages are loaded when we run the code below: 

```{r eval = F}
library(tidymodels)
```

One of these packages is the `infer` package, which is used to conduct simulation-based inference in R.

# Define inference task

First define the inference task you're doing:

- Confidence interval: To estimate a parameter of interest
- Hypothesis testing: To assess a claim about a population parameter

## Confidence intervals

The general structure of `infer` code to generate the bootstrap distribution for confidence intervals is 

```{r}
boot_dist <- df %>%
  specify(...) %>%
  generate(...) %>%
  calculate(...)
```

Let's break down each line of code: 

## `specify`

To determine the arguments for the `specify` function, you need to determine two things: 

1. Are you doing one- or two-sample inference?
2. Is the primary variable of interest, i.e. the response variable, quantitative or categorical? 

### One-sample inference 

#### Quantitative variable of interest 

If we're conducting one-sample inference for a quantitative variable, `[NUM_VAR]`, we will use the following code: 

```{r}
specify(response = [NUM_VAR])
```

#### Categorical variable of interest 

If we're conducting one-sample inference for a categorical variable, `[CAT_VAR]`, we will use the following code:

```{r}
specify(response = [CAT_VAR], success = "CATEGORY")
```

where "CATEGORY" is the specific category of the variable we're studying.


### Two-sample inference

#### Quantitative response + Categorical grouping variable

If we're conducting two-sample inference for a quantitative variable of interest, `[NUM_VAR]`, with a categorical variable defining the groups, `[CAT_VAR]`, we use the following code:

```{r}
specify(response = [NUM_VAR], explanatory = [CAT_VAR])
```

#### Categorical response + Categorical grouping variable

If we're conducting two-sample inference for a categorical variable of interest, `[CAT_VAR1]`, with a categorical variable defining the groups, `[CAT_VAR2]`, we use the following code:

```{r}
specify(response = [CAT_VAR1], explanatory = [CAT_VAR2], success = "CATEGORY1")
```

where "CATEGORY1" is the category of `[CAT_VAR1]` we're analyzing.

#### Two quantitative variables

If we're conducting two-sample inference for the association between two quantitative variables, `[NUM_VAR1]`, with a categorical variable defining the groups, `[NUM_VAR2]`, we use the following code:

```{r}
specify(response = [NUM_VAR1], explanatory = [NUM_VAR2])
```

\newpage 

## `generate`

Since the goal of the confidence interval is to use the sample data to estimate a plausible range of values the parameter can take, we will use the code below to indicate we want to take a bootstrap sample of the data:

```{r}
generate(reps = N, type = "bootstrap")
```

where `N` is the number of reps you want to use to generate the bootstrap distribution. 


## `calculate`

This is where we define the statistic to calculate in each iteration. 

```{r}
calculate(stat = "_______")
```

For example, if we're constructing a confidence interval for the population mean, we will use the code below:

```{r}
calculate(stat = "mean")
```

Type `??infer::calculate` in the console to see the options for statistics that we can calculate.


